{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-15 paper/paper.tex
added constraints for the scheduler (informaly)
added comment about interleaving threads
rephrased comment about interleaving threads
use package todonotes
added todo: program execution

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}

@@

>>>>

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}

@@

\begin{enumerate}
\item It always picks an active thread
\item If there is a hidden thread, always choose high or always high threads
\item Only use low information and the low part of the history to choose a 
      new thread
\end{enumerate}

In constraint two the interleaving of always high threads is realized.

\todo{Explain how the programs are executed}
